\documentclass{article}

\usepackage{geometry}
\usepackage{hyperref}

\title {Khidmat: DYSF IT Revampment}

\author{
  Sameer Anees Jaliawala\\ sj02732 
}
\date{}  

\begin{document}
\maketitle

% Use first person plural (we, us) even if you did the Khidmat individually.

% An introduction of the project, no more than 2 sentences. Provide the highest level of detail only. Other details will come later.
% Typically, "This project is to <short description of porject> for/at <client>."
This project is to revamp the IT system of Dhoraji Youth Service Foundation. Our main objective is to create an Award Management System; furthermore, we will be involved in all other side projects related to IT such as the DYSF Portal and the Scholarship Management System.  

% About the client.
DYSF is a non-profit organization that represents the Dhoraji Memons and the youth of the community. DYSF's mission is to strive for transformation of dhoraji memons into a highly educated, self reliant, progressive and healthy community. More On:\newline \href{http://www.dhorajiyouth.org/aboutus.aspx?page=about}{http://www.dhorajiyouth.org/aboutus.aspx?page=about}

% About the project.
DYSF has a an award ceremony every year where hundreds of dhoraji memon students from all education background receive awards for their achievements in their studies. However, most of the system relies on manual entry of paper based forms and the use of excel to generate lists which is a highly inefficient system in this technologically advanced era. Our objective is to make an efficient system, that makes use of database technology, which could ease the overall process. Moreover, we would also give our contributions to IT related projects that will be taking place during our khidmat which are: The DYSF Portal and the DYSF Scholarship Management System. All the work will be done by the DYSF IT Team, which includes us.

% About the plan of work.
We will work part time for DYSF under the supervision of their IT supervisor, who is one of their board of governors. Our main work would take place at our own convenient time and place and their is no particular deadline set for the project. The goal is to develop, test, and deploy the award management system by the end of our Khidmat.

% Copy-paste this section with necessary modifcations for each week.
\newpage % Start the report for each week on a new page.
\section*{Week 1: 27--2 June, 2018}

% A summary, maximum 2 sentences, of this week's activities.
We spent this week meeting the IT team we would work with. We laid down objectives and aims and also decided on the division of labour. We checked out the annual award's current manual system, as well as the inoperative DYSF scholarship system at the DYSF office. We also paid a visit to Expertek Solutions, the firm which handled all their IT business and also made their website. \newline

\begin{tabular}{|l|l|l|l|}
  \hline
  Item 	& Activity & Time & ID \\\hline\hline
  1	& Met IT team and supervisor & 2 hrs & sj02732 \\\hline
  2	& Checked out the current IT system at DYSF office & 2 hrs & sj02732 \\\hline
  3	& Meeting at Expertek Solutions & 2 hrs & sj02732 \\\hline
  4 & Research, Brainstorming, Learning html,css,php & 1hr and 30mins & sj02732  \\\hline
\end{tabular}
\newline
The total time spent on the Khidmat this week is as follows.

\begin{tabular}{|l|l|}
  \hline
  ID & Total Hours\\\hline\hline
  sj02732 & 7 hours and 30 mins\\\hline
\end{tabular}

% Other weeks ...
\newpage % Start the report for each week on a new page.
\section*{Week 2: 3--9 June, 2018}

% A summary, maximum 2 sentences, of this week's activities.
Meeting with the external supervisor. He wanted to know what we thought of the current award system and how we can improve it. We told him about our ideas and how we can make the system better. We also explained the problems about the scholarship system. We made a draft ERD of the award system. The IT team met together to bring up a lsit of problems and objectives. \newline

\begin{tabular}{|l|l|l|l|}
  \hline
  Item 	& Activity & Time & ID \\\hline\hline
  1	& Met IT team and supervisor & 2 hrs & sj02732 \\\hline
  2	& Making draft ERD and learning php,html,css & 3 hrs & sj02732 \\\hline
  3	& 1st kickstart meeting with IT team & 2 hrs & sj02732 \\\hline
\end{tabular}
\newline
The total time spent on the Khidmat this week is as follows.

\begin{tabular}{|l|l|}
  \hline
  ID & Total Hours\\\hline\hline
  sj02732 & 7 hrs\\\hline
\end{tabular}

\newpage % Start the report for each week on a new page.
\section*{Week 3: 10--16 June, 2018}

% A summary, maximum 2 sentences, of this week's activities.
Created database on the base of the draft ERD made last week. We also made ourselves aware of PHP myadmin and its database operations. We made our own effort on the user end forms. We divivded the forms into 4 parts and worked on the first part. \newline

\begin{tabular}{|l|l|l|l|}
  \hline
  Item 	& Activity & Time & ID \\\hline\hline
  1	& Created Database on PHP myadmin & 3 hrs & sj02732 \\\hline
  2	& Made user-end form on html and linked it with database(PHP) & 3 hrs & sj02732 \\\hline
\end{tabular}
\newline
The total time spent on the Khidmat this week is as follows.

\begin{tabular}{|l|l|}
  \hline
  ID & Total Hours\\\hline\hline
  sj02732 & 6 hrs\\\hline
\end{tabular}

\newpage % Start the report for each week on a new page.
\section*{Week 4: 17--23 June, 2018}

% A summary, maximum 2 sentences, of this week's activities.
We made 2 more user-end forms out of the 4 forms. We added validation checks and added final queries to them.  \newline

\begin{tabular}{|l|l|l|l|}
  \hline
  Item 	& Activity & Time & ID \\\hline\hline
  1	& Made 2 more user-end forms on html & 3-4 hrs & sj02732 \\\hline
  2	& Added sql queries and validation checks. Testing and debugging. & 3-4 hrs & sj02732 \\\hline
\end{tabular}
\newline
The total time spent on the Khidmat this week is as follows.

\begin{tabular}{|l|l|}
  \hline
  ID & Total Hours\\\hline\hline
  sj02732 & 7 hrs\\\hline
\end{tabular}

\newpage % Start the report for each week on a new page.
\section*{Week 5: 24--30 June, 2018}

% A summary, maximum 2 sentences, of this week's activities.
Meeting with the external supervisor. We updated him about our work. The IT team told us to leave the user-end for now and to focus on the admin-end of the system. We decided we would work on Laravel and use AdminLTE as the template. We also had an internal meeting with the IT team. (This was the first time we met after Eid) \newline

\begin{tabular}{|l|l|l|l|}
  \hline
  Item 	& Activity & Time & ID \\\hline\hline
  1	& Met IT team and supervisor & 2 hrs & sj02732 \\\hline
  2	& 2nd kickstart meeting with IT team & 2 hrs & sj02732 \\\hline
  3	& Researched Laravel and implemented AdminLTe on our systems & 3 hrs & sj02732 \\\hline
\end{tabular}
\newline
The total time spent on the Khidmat this week is as follows.

\begin{tabular}{|l|l|}
  \hline
  ID & Total Hours\\\hline\hline
  sj02732 & 7 hrs\\\hline
\end{tabular}

\newpage % Start the report for each week on a new page.
\section*{Week 6: 1--7 July, 2018}

% A summary, maximum 2 sentences, of this week's activities.
Our IT Team head advised us to use Stack template instead as it had better security. We went ahead and implemented on our system. We brainstormed how the system would look like on the template and also brought up some ideas on the dashboard. We started making the first CRUD on the system ( the CRUD related to the table known as Awardees). \newline

\begin{tabular}{|l|l|l|l|}
  \hline
  Item 	& Activity & Time & ID \\\hline\hline
  1	& Implemeted and brainstormed on Stack template and its usage & 2 hrs & sj02732 \\\hline
  2	& Started making the first CRUD of the system & 3 hrs & sj02732 \\\hline
\end{tabular}
\newline
The total time spent on the Khidmat this week is as follows.

\begin{tabular}{|l|l|}
  \hline
  ID & Total Hours\\\hline\hline
  sj02732 & 5 hrs\\\hline
\end{tabular}

\newpage
\section*{Conclusion}

% Remind the reader about the project. Summarise your activities over the course of the project.


\newpage
% Show your external supervisor your report, especially the weekly upates; have them sign a printed copy of this page; scan the signed page; and include the scanned page in this document as an image.

I hereby certify that I supervised this Khidmat and that I have read and agree with the weekly updates included in the Khidmat report.\\[50pt]

\noindent\begin{tabular}{@{}p{.6\textwidth}@{\hspace{.1\textwidth}}p{.3\textwidth}}
  \hrulefill &   \hrulefill \\
  Name and signature & Date and place
\end{tabular}

\end{document}
